Most of us have probably used a calendar before in our lives, even if just for home, school or work. Let's be honest, they're boring. Calendar apps can be viewed just as a list of appointments, and in an inefficient way. You need to find a meeting time, enter the information and upload it. Then the app loads the remaining available time and you either have to highlight the next time you want to attend, or see the next appointment.
The way you set up your academic calendar can have a major impact on how much work you actually get done. By identifying how much time you can give to each task in each class, you'll be able to schedule your workload more efficiently, set up meaningful group projects, and study efficiently at the end of the week.
Even more so than the setup of the calendar is the structure of the calendar which is a typical given. We see these months days and years to fill up but we dont exacatly know with what. Or even have the dedication to keep this digital planner filled with quality date that we can refer to in the future leaving our calendar to be a wasteland for potenetial in the Information age when we can do so much more with it.
I am proposing a calendar that links data and information together in a holistic way that the user of such a tool can without fear plan and organize and review their events.
The calendar will have access to smart health device data and or smart phone device data to get the amount of steps the user has taken, the heart rate of the user and the sleep of the user if accessible and lastly the location data as well.
There are privacy concerns when you talk about data such as listed about but the application it self will only be OSS so any malicious intent will be seen in the implementation and changed at once.
The calendar will be based solely on the user of the application, nothing or no one else.
